In most applied sciences,
it has become common publication practice to provide evidence of the
statistical or laboratory data underlying the conclusions. This is done
to support reproducibility and replicability of the scientific
findings. 
Journals with a
data deposit policy have stored the supplementary materials on journal
websites, often as simple web-based ZIP archives. While ensuring that
the materials are preserved as long as the journal is active
(\textit{permanence}) and are accessible to any reader of the original article (\textit{accessibility}), certain shortcomings became
apparent. Very large datasets and datasets with confidentiality concerns
were nearly always out of scope. 

More recently, journals have leveraged
either dedicated, journal-branded views onto larger archives (e.g,
Dataverse, Figshare), built their own data archive infrastructure
(\urlcite{https://www.elsevier.com/authors/author-services/research-data}{Elsevier/Mendeley}), or have allowed for data and code to be stored
more generally on any of a curated list of trusted%
\footnote{CoreTrustSeal, \url{https://www.coretrustseal.org/}}
or approved
whitelist of third-party repositories.%
\footnote{\url{https://f1000research.com/for-authors/data-guidelines}, \url{https://www.nature.com/sdata/policies/repositories}}
Each of these alternatives rely
on a journal or publisher vetting the repositories and ascertaining
that it meets some set of criteria, or relying on third-party vetting of
repositories exists, such as CoreTrustSeal.%
\footnote{\url{https://www.coretrustseal.org/}} 
For instance, \cite{NatureScientificData2019} assesses relevance to the community, cost to researchers, data access conditions, repository longevity, data persistence and versioning. \cite{CoreTrustSealCoreTrustSeal2017} assesses similar criteria, as well as policies surrounding a set of requirements. The presence on a list of recommended data repositories, or a successful CoreTrustSeal certification, are strong indicators of robust and persistent archives.

However, in our experience \parencite{VilhuberAEAPap.Proc.2020,Kingi2018}, only a few of the holders of restricted-access data appear on such lists. Large survey institutions, many national statistical offices, and nearly all private-sector holders of restricted-access data provide some information about accessibility, but nearly no (publicly accessible) information about data persistence, versioning, or citability of their data assets. While publishers and (some) funders expect that repositories support researchers in making data FAIR, many data providers have yet to respond. In some cases, data access by researchers is incidental, and data providers are not responsive to FAIR considerations, in particular for private sector and sub-national providers of administrative data. Even at the national level,   regulations in various countries that aim to improve access to and preservation of data assets for research are very recent (Digital Economy Act of 2017 in the UK, Loi pour une République Numérique 2017 in France, and the Foundations for Evidence-Based Policymaking Act of 2018 in the United States, to mention only a few examples), and have yet to make a measurable impact. 

Even when data are public-use, or even when the repository is indexed in re3data,\footnote{\url{https://www.re3data.org}} information about accessibility and permanence are incomplete or wrong. Institutions are also able to list multiple access and preservation policies, leaving it open which policy applies to a particular data object. See the Appendix for additional details.

%In all cases known to us, the support for restricted-access
%repositories is quite limited. Thus, most of the known support for
%third-party repositories does not provide much information about
%accessibility (the presumption is that access is open), nor about the
%permanence of the repositories - this is presumably one of the
%evaluation criteria that journals and publishers use, but is not clearly
%defined as such. 
%In fact, at least one of the consulted publishers
%explicitly allows for quite transitory repositories for code, without
%clearly distinguishing that from archives that are more permanent.%
%\footnote{F1000Research (\url{https://f1000research.com/for-authors/data-guidelines}) allows for code deposits through github.com, which has no mandate to preserve, and allows code owners to delete materials at any time without restrictions.}

To a large extent, the onus on reporting on these facets of data archives falls onto the researcher who uses these data, and will continue to do so for considerable time. 
%
Nevertheless, much of the information about persistence of archives and
materials stored within those archives is available, albeit in
idiosyncratic and non-machine readable form. Consider only the case of
national archives (e.g., the \urlcite{https://www.archives.gov/dc/researcher-info}{U.S. National Archives} or the \urlcite{http://www.archives-nationales.culture.gouv.fr/}{\textit{Archives Nationales} in France}). 
In general, data stored in national archives is
permanently archived; if it is not, this is clearly documented.%
\footnote{For instance, the program code for the Business Register is destroyed when a new system is put in place - they are never kept \parencite{U.S.CensusBureauRecordsControlSchedule2009}. Unedited master files for the American Community Survey are destroyed 6 years after the Edited master files are verified, unless still needed ``for Census operations'' \parencite{U.S.CensusBureauRecordsControlSchedule1999}.}
Furthermore, access is generally not restricted - if it is, this is
clearly documented. However, materials in national archives do have
certain restrictions - they may require sending in a written request, or
a physical visit to a location with copies of the data. Thus, while the
information may satisfy the publication requirements of even the most
open journal, there is no robust and standardized way of documenting the
additional restrictions on access that persist. 

In proposing the
metadata package outlined in this article, we attempt to improve on this
situation. By providing a sparse but sufficient encapsulation of the
information collected from authors, archives, and other third-parties,
we create greater transparency about the data supporting the research.
By relying on existing metadata schemas and metadata content, we
minimize the effort by all parties involved, increasing the likelihood
of adoption. And by intrinsically addressing the possibility that the
information obtained at the time of publication may differ from that returned by later
requests for the same information, we provide the tools to journals,
publishers, and their editors to document that the decision to publish
was based on adequate information at the time of the publication (or
acceptance decision).

